\documentclass[a4paper, oneside]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{hyperref}

\begin{document}

\chapter{How to: Boot the HAW-Shell}
\section{File CY7C64225\_Setup\_Guide\_1\_3-1.pdf}
\url{http://zedboard.org/sites/default/files/documentations/CY7C64225_Setup_Guide_1_3-1.pdf}
\begin{itemize}
\item This file contains Information about the drivers you need to install
\item \textbf{when using a windows systems. It should not be required running windows 7+.}
\end{itemize}

\section{File GS-AES-Z7EV-7Z020-G-V7-1.pdf - Page 11}
\url{http://zedboard.org/sites/default/files/documentations/GS-AES-Z7EV-7Z020-G-V7-1.pdf}
\begin{itemize}
\item This page contains the Basic Setup and Operation
\item Page 38 contains infos on the usage of USB-UART
\end{itemize}

\section{Here are the needed step to run a custom build (HAWShell) :}
\begin{enumerate}
\item Put the custom image on the root SD Card
\item Connect 12 V power to barrel jack (J20).
\item Connect the UART port of ZedBoard TM (J14) to a PC using the MicroUSB cable.
\item Insert the included SD Card into J12.
\item Turn power switch (SW8) to ON. Board will power on. Green Power Good LED (LD13) should illuminate.
\item Wait approximately 15 seconds. The blue Done LED (LD12) should illuminate, and a default image will be displayed on the OLED (DISP1).
\item If the amber USB-Link Status (LD11) does not flicker to indicate activity, instructions for downloading the CY7C64225 USB-to-UART driver can be found on the website listed below.
\item Use Device Manager to determine the COM Port. Open a Terminal Program, confi gure to 115200/8/n/1/n.
\item Cycle power by turning the power switch (SW8) from ON to OFF and then back ON.
\item In the Terminal Window, a simple Linux image should boot with functionality that demonstrates the basic capabilities of ZedBoard TM .
\item When you are done using Linux, run the command “poweroff” and then switch off ZedBoard TM .
\end{enumerate}

\end{document}